### 2016-01-16 paper.tex
Shorten title; towards #37

{\Large \textbf\newline{Measurements on a 1:6 scale DOE Reference Model 2
cross-flow hydrokinetic turbine at transitional Reynolds numbers: Power production,
near-wake dynamics, and blade support strut losses}}
\newline
% Insert author names, affiliations and corresponding author email (do not include
% titles, positions, or degrees).
\\
Peter Bachant\textsuperscript{1,*},
Martin Wosnik\textsuperscript{1},
Budi Gunawan\textsuperscript{2},
Vincent Neary\textsuperscript{2}
\\
\bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham, NH,
USA
\\
\bf{2} Water Power Technologies, Sandia National Laboratories, Albuquerque, NM, USA
\\
\bigskip

>>>>

{\Large \textbf\newline{Experimental investigation of a low solidity cross-flow
        turbine at transitional Reynolds numbers: Power production, near-wake dynamics,
        and blade support strut losses}} \newline
% Insert author names, affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1}, Budi
Gunawan\textsuperscript{2}, Vincent Neary\textsuperscript{2} \\ \bigskip \bf{1}
Center for Ocean Renewable Energy, University of New Hampshire, Durham, NH, USA
\\ \bf{2} Water Power Technologies, Sandia National Laboratories, Albuquerque,
NM, USA \\ \bigskip
